---
title: "Reflection on R"
author: "Jessica Ayers"
date: "2023-06-27"
---

```{r, eval = FALSE, echo = FALSE}
rmarkdown::render("/Users/jessayers/Documents/ST 558/TOPIC 2/blog/_Rmd/2023-06-27-third.Rmd",
output_format = "github_document",  
output_dir = "/Users/jessayers/Documents/ST 558/TOPIC 2/blog/_posts" ,
output_options = list(html_preview = FALSE))
```

```{r, echo = FALSE}
knitr::opts_chunk$set(fig.path = "../images/")
```

## Reflection Post

I have worked with R in many statistics classes thus far in my academic career, but being exposed to the amount of different visuals that can be created for different processes has been the coolest thing I have learned about programming in R. Making an ordinary plot is mostly simple, but creating a plot with color, groups, different attributes, etc takes more time. In this past module 8, there was one visual that I found very interesting. It shows a regression trend for different prediction values. 

Using the Seoul Bike Data:

```{r, message = FALSE}
library(ggiraphExtra)
library(tidyverse)
bikeData <- read_csv("/Users/jessayers/Documents/ST 558/TOPIC 3/SeoulBikeData.csv",  locale=locale(encoding="latin1"))
bikeData
```

Similar to homework 8, we can turn the rented bike counts variable into a binary 0/1 for counts of over 700.

```{r}
bikeData$count <- 0
for(i in 1:nrow(bikeData)){
  if(bikeData$`Rented Bike Count`[i]>=700){
    bikeData$count[i] <- 1
  }
  else{
    bikeData$count[i] <- 0
  }
}

bikeData <- bikeData %>%
  rename("Temp" = "Temperature(°C)")
```

Now we can fit a poisson model using `count` as the response variable and `temperature` and `holiday` as the predictor variables.

```{r}
glmFit <- glm(count ~ Temp*Holiday, data = bikeData, family = "binomial")
```

Now we can plot the predicted values of this regression.

```{r, warning = FALSE}
ggPredict(glmFit)
```