---
title: "Programming Background"
author: "Jessica Ayers"
date: "2023-06-06"
---

```{r, echo = FALSE, eval = FALSE}
rmarkdown::render("/Users/jessayers/Documents/ST 558/TOPIC 2/blog/_Rmd/2023-06-08-second.Rmd",
output_format = "github_document",  
output_dir = "/Users/jessayers/Documents/ST 558/TOPIC 2/blog/_posts" ,
output_options = list(html_preview = FALSE))  
```

```{r, echo = FALSE}
knitr::opts_chunk$set(fig.path = "../images/")
```

## Prompt

**Everyone in this course had some programming experience coming in (due to the prerequisites).  What are your thoughts on R vs whatever other software you've used?  What functionality do you like about R?  What parts do you miss about your other language?  Do you consider R a difficult language to learn? (If you knew R prior to the course, describe your experience when first learning it.)**

The majority of my programming experience has been in either SAS or R. I've worked with SAS more, but I have seen that many individuals in the work force rely on R more. That is one of the major reasons that I am taking this class; to be proficient in SAS and R is my goal. One thing I like about R is how organized everything can be. With access to R projects, R Markdown, and using R script, I can work with data easily. One thing I miss about SAS is that it is not case sensitive. I think R takes practice. Similar to many programming languages, the foundation is very similar across languages, but the specifics are different. The more you work with it, the easier it becomes!

## Example Output from R Markdown

```{r}
plot(mtcars)
```