---
title: "Vignette Blog Post"
author: "Jessica Ayers"
date: "2023-06-22"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(fig.path = "../images/") 
```

```{r, eval = FALSE}
rmarkdown::render("/Users/jessayers/Documents/ST 558/TOPIC 2/blog/_Rmd/2023-06-22-my-new-blog-post.Rmd",
output_format = "github_document",  
output_dir = "/Users/jessayers/Documents/ST 558/TOPIC 2/blog/_posts" ,
output_options = list(html_preview = FALSE))
```

Once you’ve completed your vignette you should write a brief blog post:

  - explaining what you did in the project and any interesting findings
  - You should also reflect on the process you went through for this project. Discuss things like:
    - what was the most difficult part of the logic and programming for you?
    - what would you do differently in approaching a similar project in the future?
  - In your blog post, provide a link to your github pages repo and the regular repo (non- github pages site) as well! The URL to this (rendered) blog post is what you will submit at the project assignment link.